\section{Description of the data sets}

The input features for all molecules in the data set were 512-bit Morgan circular fingerprints\cite{Rogers_2010}, calculated with a bond radius of 2, and derived from the canonical smiles, implemented in the RDkit\cite{rdkit}.

\textbf{Harvard Clean Energy Project}:The Clean Energy Project is the world's largest materials high-throughput virtual screening effort\cite{hachmann_lead_2014,hachmann_harvard_2011}, and has scanned more than 3.5 million molecules to find those with high power conversion efficiency (PCE) using quantum-chemical techniques, taking over 30,000 years of CPU time. The target value within this dataset is the power conversion efficiency (PCE), which is calculated for the 2.3 million publicly released molecules, using the Scharber model\cite{scharber_design_2006} and frontier orbitals calculated at the BP86\cite{perdew_density-functional_1986,becke_densityfunctional_1993}\/def2-SVP\cite{weigend_balanced_2005} level of theory.


\textbf{Dose-Response Data Set}:These data sets were obtained from the NCI-cancer database\cite{_nci_}.  The dose-response target value has a potential range of -100 to 100, and reports a percentage cell growth relative to a no-drug control.  Thus, a value of +40 would correspond to a 60\% growth inhibition and a value of -40 would correspond to 40\% lethality.  Molecules with a positive value for the dose-response are known as inhibitors, molecules with a score less than 0 return a cytotoxic effect. Results against the NCI-H23 cell line was taken against a constant log(concentration) of -8.00M and where multiple identical conditions were present in the data, an average was used.  It should be noted that for this data set, we assert smaller values represent a more desirable outcome. 


\textbf{Malaria Data Set}:The Malaria data set was taken from the \textit{P. falciparum} whole cell screening derived by combining the GSK TCAMS data set, the Novatis-GNF Malaria Box data set and the St Jude's Research Hospital data set, as released through the Medicines for Malaria Venture website \cite{23798988}.  The target is the EC50 value, which is defined as the concentration of the drug which gives half maximal response.  Much like the Dose response set, this is a minimization problem; the lower the concentration, the more potent the drug.
